---
title: "Team UTD Dashboard"
format: 
  dashboard:
    theme: united
    orientation: rows
---

Project Dashboard for Team UTD: Analyzing World data and GPD and Health

# chart 1

Part 1: descriptives

## {.sidebar}

This is a sidebar. 

## Midwest data

Demographic information of midwest counties from 2000 US census

This dashboard uses the `midwest` dataset from the `ggplot2` package to create an interactive box plot showing the percentage of college-educated individuals (`percollege`) across different states.

```{r}
#| message: false
#| warning: false
library(plotly)
fig <- plot_ly(midwest, x = ~percollege, color = ~state, type = "box")
fig
```

## Gapminder data


Use Gapminder data to illustrate interactive charts.  Note the font use, color choices and animation button and slider control.

```{r  message=FALSE}

#install.packages("gapminder")
library(gapminder)
library(RColorBrewer)
library(plotly)

# Read in Gapminder data
df <- gapminder 

# Font management

t <- list(
  family = "corgaramond",
  size = 12)

# Create figure object
fig <- df %>%
  plot_ly(
    x = ~gdpPercap, 
    y = ~lifeExp,
    size = ~pop, 
    color = ~continent, 
    colors = c("slateblue3", "steelblue", "firebrick", "forestgreen", "turquoise1"), 
        # manually select colar 
    alpha=.5, # translucent glyth
    frame = ~year, 
    text = ~country, 
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers',
    fill = ~''
  )

# Add font to text
fig <- fig %>% layout(
  xaxis = list(
    type = "log"
  ), font = t
)


fig <- fig %>% layout(legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5, y = 100))             # put legend in center of x-axis

fig <- fig %>% animation_button(
  x = 1, xanchor = "right", y = 0, yanchor = "bottom"
)
fig <- fig %>% animation_slider(
  currentvalue = list(prefix = "YEAR ", font = list(color="red"))
)
fig


```


# chart 2

Part 2: Relationship

```{r}
plotly::plot_ly(
  data = mtcars,
  x = ~wt,
  y = ~mpg,
  type = 'scatter',
  mode = 'markers',
  color = ~as.factor(cyl),
  marker = list(size = 10,
                opacity = 0.5,
                line = list(width = 2,
                            color = 'rgb(0, 0, 0)'))
)
```